---
title: "Soil Carbon Calculations"
author: "Clare"
date: "16/08/2021"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(SoilR, ggplot2, dplyr, tidyr, soilassessment, deSolve, readr, pracma, jsonlite, kableExtra)

working_dir <- getwd()

source(file.path(working_dir, "model_functions.R"))
source(file.path(working_dir, "estimate_carbon_input.R"))
source(file.path(working_dir, "uncertainty_functions.R"))


crop_data <- clean_crop_variable_data(crop_data = read_csv("data/crop_values.csv", col_types =  "cdddd"))
tilling_factors <- read_csv("data/tilling_factors.csv", col_types = "cccd") 

```

## Inputs

There are various inputs you need to specify. The following code calculates the minimum and maximum expected results with a 90% confidence interval. The variables tested here include the soil organic carbon, soil clay content and the yield. These need to be calculated and then the yield values returned to the parameter file. 

```{r inputs_uncertainty_analysis, echo=FALSE, warning=FALSE}

# Set the project name, and the farm location - this must be the same name as a local weather station
# TODO: get Tim's code to locate the closest weather station 
project_name <- "dobimar"
farm_location <- "Schwerin"

# Constant variables
# Set these once here. 
hectares <- 72
soil_thick <- 25
pE <- 1    # Evaporation coefficient - 0.75 open pan evaporation or 1.0 potential evaporation
time_horizon <- 10
field_id <- 1 # If more than one field, need to update code. 

# Add in the values obtained from the soil lab
# These values are added automatically to the uncertainty analysis
# soc_samples <- c(34.62, 34.21, 34.51, 28.17, 31.20)
soc_perc <- c(1.1, 1.1, 1.1, 0.9, 1) # %
clay_samples <- c(17, 6, 11, 9, 9) # %
bulk_density_samples <- c(1259, 1244, 1255, 1252, 1248) #kg/m3

soc_stock <- soil_thick/100 * soc_perc/100 * bulk_density_samples * 10000/1000 # tC/ha

clay_bounds <- calculate_confidence_interval(clay_samples)
soc_bounds <- calculate_confidence_interval(soc_stock)

mean_soc_perc <- mean(soc_perc)
mean_clay <- mean(clay_samples)
mean_soc <- mean(soc_stock)

# Add additional yields as necessary
# Convert the values to kg/ha
yield_rape <- c(51.15, 42.01, 32.9, 36.04)*.1*1000 
yield_wheat <- c(98.02, 85.87, 92.71, 78.23, 67.55)*.1*1000

# Add the following to the carbon_inputs csv file
# These represent the minimum, maximum expected values within a 90% confidence interval
yield_rape_bounds <- calculate_confidence_interval(yield_rape)
yield_wheat_bounds <- calculate_confidence_interval(yield_wheat)

# Also add these values to the carbon_inputs csv file 
mean_rape <- mean(yield_rape)
mean_wheat <- mean(yield_wheat)

inputs_table <- c("Project Name " = project_name,
                  "Project Location" = farm_location,
                  "Field Size" = hectares,
                  "Analysis Time Horizon" = paste0(time_horizon, " years"),
                  "Average starting SOC %" = paste0(mean_soc_perc, " %"),
                  "Average starting SOC" = paste0(round(mean_soc,1), " tC/ha"),
                  "Average clay content" = paste0(mean_clay, " %"))

inputs_table %>% kable(caption = "Project Input Parameters") %>% kable_styling()

```


## Project Parameters

Within the parameter_file folder, you should create parameter files for the field and carbon inputs, representing the holistic management practices expected over the next 10 years. 

```{r parameters, echo=FALSE, warning=FALSE}

if(!dir.exists(file.path("results", project_name))){dir.create(file.path("results", project_name))}
if(!dir.exists(file.path("plots", project_name))){dir.create(file.path("plots", project_name))}

weather_data <- read.csv(paste0("data/weather_average/",tolower(farm_location),"_uncertainty.csv"))

field_parameters <- read_csv(file.path(working_dir, "parameter_files", paste0(project_name,"_field_parameters.csv")),
                             col_types = "dcccdddddcllllllllllll")

field_parameters$climate_zone <- tolower(field_parameters$climate_zone)

field_parameters <-  field_parameters %>% 
  left_join(tilling_factors, by = c("climate_zone", "tilling" = "new_practice")) %>% 
  rename(tilling_factor = factor)

field_parameters <- get_bare_profile_df(field_parameters)


carbon_input_data <- read_csv(file.path(working_dir, "parameter_files", paste0(project_name,"_carbon_inputs.csv")),
                              col_types = "dccddddddddddddddd") 

check_field_differences(field_parameters, carbon_input_data)

carbon_input_data <- clean_carbon_input_data(carbon_input_data, crop_data) 

carbon_inputs <- summarise_carbon_inputs(carbon_input_data,
                                         crop_data)

fields <- carbon_inputs %>% select(field_id, case) %>% distinct()

uncertainty_list <- expand.grid(
  "field_id" = unique(fields$field_id),
  "case" = unique(fields$case),
  "clay" = clay_bounds,
  "soc" = soc_bounds,
  "carbon_inputs" = c("min_yield", "max_yield"),
  "evap" = c("min_evap", "max_evap"),
  "temp" = c("min_temp", "max_temp"),
  "precip" = c("min_precip", "max_precip")
)  

uncertainty_list <- uncertainty_list %>% 
  left_join(field_parameters %>% select(field_id, case, tilling_factor, bare_profile), by = c("field_id", "case")) %>% 
  mutate(label = 1:nrow(uncertainty_list))

```

The following table represents the holistic practices incorporated in this analysis. 

Important to note - the main parameters that can be added to reflect holistic practices currently include:
- Changes in Crop rotations, residue left of field and theoretically expected yields (currently just historic)
- Change in tilling practices: Conventional -> Reduced -> No till
- Additional Manure (no other fertilizer changes are reflected in the R model - only the LCA)
- Cover crop impact on bare soil vs covered soil (no additional Carbon inputs can be calculated at the moment)

Further research needs to be undertaken to better reflect any additional impacts that are expected. 
```{r, echo=FALSE, warning=FALSE}
crops <- carbon_input_data %>% filter(crop != "manure") %>% 
  select(case,crop, residue, contains("year")) %>% 
  mutate(residue = residue *100)


crops %>%  kable(col.names = c("Case",  "Crop", "% Residue Left", paste("Year", 1:10))) %>%  kable_styling()

```

```{r, echo=FALSE, warning=FALSE}

manure <- carbon_input_data %>% filter(crop == "manure") %>% select(case, annual_quantity)

manure %>% kable( col.names = c("Case","Manure Applied")) %>% 
  kable_styling()


```

```{r, echo=FALSE, warning=FALSE}

tilling <- field_parameters %>% select(case, tilling)


tilling %>% 
  kable(col.names = c("Case", "Tilling Method")) %>% 
  kable_styling()

```

```{r, echo=FALSE, warning=FALSE}

base_profile <- field_parameters %>% select(case, bare_profile) %>% 
  separate(bare_profile,  c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))


base_profile %>% 
  rename(Case = "case") %>% 
  mutate(Jan = cell_spec(Jan, background = ifelse(Jan == TRUE, "green", "brown")),
         Feb = cell_spec(Feb, background = ifelse(Feb == TRUE, "green", "brown")),
         Mar = cell_spec(Mar, background = ifelse(Mar == TRUE, "green", "brown")),
         Apr = cell_spec(Apr, background = ifelse(Apr == TRUE, "green", "brown")),
         May = cell_spec(May, background = ifelse(May == TRUE, "green", "brown")),
         Jun = cell_spec(Jun, background = ifelse(Jun == TRUE, "green", "brown")),
         Jul = cell_spec(Jul, background = ifelse(Jul == TRUE, "green", "brown")),
         Aug = cell_spec(Aug, background = ifelse(Aug == TRUE, "green", "brown")),
         Sep = cell_spec(Sep, background = ifelse(Sep == TRUE, "green", "brown")),
         Oct = cell_spec(Oct, background = ifelse(Oct == TRUE, "green", "brown")),
         Nov = cell_spec(Nov, background = ifelse(Nov == TRUE, "green", "brown")),
         Dec = cell_spec(Dec, background = ifelse(Dec == TRUE, "green", "brown"))) %>% 
  kable(escape = F) %>% 
  kable_styling()


```

```{r create_results, echo=FALSE, warning=FALSE}


for (i in 1:nrow(uncertainty_list)){
  
  # Set parameters
  label <- uncertainty_list$label[i]
  case <- uncertainty_list$case[i]
  soc <- uncertainty_list$soc[i]
  clay <- uncertainty_list$clay[i]
  tilling_factor <- uncertainty_list$tilling_factor[i]
  bare_profile <- uncertainty_list$bare_profile[i]
  
  starting_soil_content <- estimate_starting_soil_content(soc, clay)
  
  field_carbon_in <- carbon_inputs %>% 
    filter(name == uncertainty_list$carbon_inputs[i],
           case == !!case,
           field_id == !!field_id) %>% 
    select(carbon_inputs) %>% pull()
  
  dr_ratios <- carbon_inputs %>% 
    filter(name == uncertainty_list$carbon_inputs[i],
           case == !!case,
           field_id == !!field_id) %>% 
    select(dr_ratio) %>% pull()
  
  temp <- weather_data %>% select(uncertainty_list$temp[i]) %>% pull()
  precip <- weather_data %>% select(uncertainty_list$precip[i]) %>% pull()
  evap <- weather_data %>% select(uncertainty_list$evap[i]) %>% pull()
  
  all_c <- calc_carbon_over_time(time_horizon,
                                 field_carbon_in,
                                 dr_ratios,
                                 bare_profile,
                                 temp = temp,
                                 precip = precip,
                                 evap = evap,
                                 soil_thick = soil_thick,
                                 clay = clay,
                                 pE = pE,
                                 PS = starting_soil_content,
                                 tilling_factor)
  
  if (label == 1){
    all_results <- data.frame(V1 = all_c$TOT)
  }else{
    all_results[label] <- all_c$TOT
  }
  
  
}


# Set parameters
case_list <- field_parameters$case

for(case in case_list){
  soc <- mean_soc
  clay <- mean_clay
  tilling_factor <- field_parameters$tilling_factor[field_parameters$case == case]
  bare_profile <- field_parameters$bare_profile[field_parameters$case == case]
  
  starting_soil_content <- estimate_starting_soil_content(soc, clay)
  
  field_carbon_in <- carbon_inputs %>% 
    filter(name == "mean_yield",
           case == !!case,
           field_id == !!field_id) %>% 
    select(carbon_inputs) %>% pull()
  
  dr_ratios <- carbon_inputs %>% 
    filter(name == "mean_yield",
           case == !!case,
           field_id == !!field_id) %>% 
    select(dr_ratio) %>% pull()
  
  temp <- weather_data %>% select(mean_temp) %>% pull()
  precip <- weather_data %>% select(mean_precip) %>% pull()
  evap <- weather_data %>% select(mean_evap) %>% pull()
  
  all_c <- calc_carbon_over_time(time_horizon,
                                 field_carbon_in,
                                 dr_ratios,
                                 bare_profile,
                                 temp = temp,
                                 precip = precip,
                                 evap = evap,
                                 soil_thick = soil_thick,
                                 clay = clay,
                                 pE = pE,
                                 PS = starting_soil_content,
                                 tilling_factor)
  
  
  
  if (case == "base"){
    all_results["base"] <- all_c$TOT
  }else if (case == "regen"){
    all_results["regen"] <- all_c$TOT
  }
  
}

```

## Results

The following table is a summary of the main changes in values for both the base (business as usual) case and the regenerative case. The variance value represents the maximum % difference between the maximum value  expected with a 90% confidence interval and the regen case results. 

```{r, echo=FALSE, warning=FALSE}
## Results summary


all_results$time <- 1:nrow(all_results)/12
all_results_long <- pivot_longer(all_results ,  cols = contains("V"))


all_results_time <- all_results_long %>% 
  group_by(time) %>% 
  summarise(max_val = max(value),
            min_val = min(value), 
            .groups = "drop") %>% 
  left_join(all_results %>% select(time, base, regen), by = "time") %>% 
  mutate(var_max = (max_val - regen)/regen,
         var_min = (min_val - regen)/regen)

res_start <- head(all_results_time, 1)
res_end <- tail(all_results_time, 1)

baseline_change <- res_end$base - res_start$base
baseline_change_perc <- ((res_end$base - res_start$base)/res_start$base)*100
regen_change <- res_end$regen - res_start$regen
regen_change_perc <- ((res_end$regen - res_start$regen)/res_start$regen)*100


variance_upper <- res_end$var_max * 100
variance_lower <- res_end$var_min * 100

res <- c("Final SOC Base" =  paste0(round(res_end$base, 1), " tC/ha"),
         "Final SOC Regen" =  paste0(round(res_end$regen, 1), " tC/ha"),
         "Absolute change Base" = paste0(round(baseline_change, 1), " tC/ha"),
         "Percent change Base" = paste0(round(baseline_change_perc, 1), " %"),
         "Absolute change Regen" = paste0(round(regen_change, 1), " tC/ha"),
         "Percent change Regen" = paste0(round(regen_change_perc, 1), " %"),
         "Max positive variance" = paste0(round(variance_upper, 1), " %"),
         "Max negative variance" = paste0(round(variance_lower, 1), " %"))

res %>% kable(caption = "Summary of Results") %>% kable_styling()

```

The following plot shows all possible trajectories of soil carbon development possible with variables within a 90% confidence interval. Ie. All possible cases have been run in which the minimum and maximum values of the clay, soil organic carbon (SOC), and carbon inputs were considered. The 90% confidence interval for monthly values for evaporation, temperature and precipitation was also varied.    

```{r, echo=FALSE, warning=FALSE}
ggplot(all_results_time)+
  geom_ribbon(aes(x = time, ymin = min_val, ymax = max_val), fill = "cornsilk")+
  geom_line(aes(x = time, y = base, colour = "black")) +
  geom_line(aes(x = time, y = regen, colour = "darkgreen"))+
  scale_x_continuous(expand = c(0, 0)) +
  theme_classic()+
  theme(legend.position = "right")+
  scale_colour_manual(name  ="Case",
                      labels = c("Base", "Regen"),
                      values=c("black", "darkgreen")) +
  labs(x = "Year", y = "Total Soil Carbon", title = "Mean Result + Uncertainty Band")

ggplot(all_results_long, aes(x = time, y = value)) + 
  geom_line(aes(colour = name))+ 
  scale_x_continuous(expand = c(0, 0)) +
  theme_classic()+
  theme(legend.position = "none")+
  labs(x = "Year", y = "Total Soil Carbon", title = "All Trajectories")

```


